Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-11-22 paper/paper.tex

\section{Introduction}
Coding is the main occupation of many people nowadays, and is also a
past-time for many too. Most people get their first steps in writing code
following the local single-threaded model. Often, it can be difficult for
beginner programmers, or even those with more experience, to abstract the key
knowledge they have obtained using this model and then apply it in a different way.

@@

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.
\section{Implementation}

\section{Evaluation}

\section{Related Work}
While other multiplayer distributed games already exist, they have not been
created with this project’s task in mind and therefore do not serve the same
purpose. They can be split into two categories – very unprofessional and too
professional. For example, hobby implementations exist that deal with
distributed problems in a bad fashion, promoting bad and incorrect programming 
practises. Similarly, a single-player-per-team distributed tic-tac-toe game in 
Java can be found online that does not comply with any design guidelines and 
puts all functionality in a single class and as such, cannot teach students good 
practice and has the potential of confusing the learner further about distributive 
programming \cite{2}.

Separately, very in-depth materials that provide state-of-the-art practices can 
be found \cite{1} but there is a high possibility that they might be incomprehensible 
to a beginner reader looking to tackle basic distributed concepts to begin with. 
Furthermore, none of the similar implementations residing on the Internet take advantage 
of the Java RMI API which must be considered a good starting point for distributed systems
learners for it to be taught as part of our degree and is a requirement for this
project. Instead, they use different sets of other technologies which can
further confuse their reader and introduce a steeper learning curve.

>>>>

\section{Introduction}
Coding is the main occupation of many people nowadays, and it is a
past-time for many too. Most beginners get their first steps in writing code
following the local single-threaded model. Often, it can be difficult for
new programmers, or even those with more experience, to abstract the key
knowledge they have obtained using this model and then apply it in a different way.

@@

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.
\section{Implementation}
The implementation follows the RMI distributed object model. A GameInt interface extends java.rmi.Remote and lists remote classes. 
A Game class implements GameInt and extends the UnicastRemoteObject. It is an analogy for what a player knows and does during a game. 
It provides an implementation for all the listed classes in the interface which include the functionality of requesting the player to make a play, 
setting the leader of the game, several methods to interact with the Role of the player and a main method that connects to other game instances. 
Currently, when running the game, the user passes it a local instance name and the name of another instance as arguments. Each instance then uses this information 
to do an RMI Registry lookup and get a reference to the other client. The Role interface allows the application to differentiate between Leader and Player classes which extend it. 
It utilises the State design pattern to allow players to seamlessly have their role changed – for example when the current leader disconnects. 
A Leader is responsible of collecting the votes from all of the members in their team in the turnStarts() method. This is done asynchronously using
a separate thread for each member – an instance of VoteThread. Each thread collects a vote from one assigned player then writes it into a corresponding position
in a shared AtomicIntegerArray that they have all been passed by the Leader. This ensures the main Leader thread can then read these values. 
Each Leader then informs all players in the game about the vote of his team. A Player instance represents a regular player that only must vote. 
Each regular player also has a mechanism to detect if a leader has not contacted them to choose a play for too long. If a time-out is triggered, 
a player calls for a new leader election. To avoid many simultaneous election calls, each regular player waits 5 minutes plus a randomised amount of time.
All plays are recorded on a GameState object instance that acts as a game board. After each turn it checks if the game is over and relays this message to the leaders
 which can then inform the members of their team.
\section{Evaluation}

\section{Related Work}
While other multiplayer distributed games already exist, they have not been
created with this project’s task in mind and therefore do not serve the same
purpose. They can be split into two categories – very unprofessional and too
professional. For example, hobby implementations exist that deal with
distributed problems in a bad fashion, promoting bad and incorrect programming 
practises. Similarly, a single-player-per-team distributed tic-tac-toe game in 
Java can be found online that does not comply with any design guidelines and 
puts all functionality in a single class and as such, cannot teach students good 
practice and has the potential of confusing the learner further about distributive 
programming \cite{MrWayFarOutYoutube15}.

Separately, very in-depth materials that provide state-of-the-art practices can 
be found \cite{DBLP:conf/nsdi/BharambePS06} but there is a high possibility that they might be incomprehensible 
to a beginner reader looking to tackle basic distributed concepts to begin with. 
Furthermore, none of the similar implementations residing on the Internet take advantage 
of the Java RMI API which must be considered a good starting point for distributed systems
learners for it to be taught as part of our degree and is a requirement for this
project. Instead, they use different sets of other technologies which can
further confuse their reader and introduce a steeper learning curve.
